Estimating duration in the presence of misclassification

### 2024-02-05 biology-data.tex
Improve chapter 2 figure

The CIS was setup in April 2020 to provide gold-standard measurements of the prevalence of SARS-CoV-2 in the community.
It is a longitudinal study with a representative sample of private households, this excludes settings such as care homes and student halls.
It is globally unique in providing a representative, longitudinal, and large-scale study.
Initially, it was limited to England, but expanded to cover the whole of the UK in September 2020.
Enrolment was continuous until 31st Jan 2022, with data collected until 13th Mar 2023~\autocite{weiRisk}.

@@

A sample of 500 randomly selected infection episodes (selected from the episodes used in the analyses in this thesis) have their test results shown in \cref{biology-data:fig:episodes}.
As can be seen, the number of tests within an episode, their length, and other characteristics vary greatly.
\begin{figure}
  \thisfloatpagestyle{empty}
  \vspace{-5cm}
  \makebox[\textwidth][c]{\includegraphics[height=.9\paperheight]{biology-data/STATS13734/data_viz}}
  \caption[CIS infection episodes]{%
    500 randomly selected infection episodes.
    Shown are the negative tests before and after the outermost positive tests associated with the episode.
    Red dots are negative tests, green dots are positive tests, and blue dots are void tests (where the result could not be determined; excluded from other analyses).

>>>>

The CIS~\autocite{CIS} was setup in April 2020 to provide gold-standard measurements of the prevalence of SARS-CoV-2 in the community.
It is a longitudinal study with a representative sample of private households, this excludes settings such as care homes and student halls.
It is globally unique in providing a representative, longitudinal, and large-scale study.
Initially, it was limited to England, but expanded to cover the whole of the UK in September 2020.
Enrolment was continuous until 31st Jan 2022, with data collected until 13th Mar 2023~\autocite{weiRisk}.

@@

A sample of 500 randomly selected infection episodes (selected from the episodes used in the analyses in this thesis) have their test results shown in \cref{biology-data:fig:episodes}.
As can be seen, the number of tests within an episode, their length, and other characteristics vary greatly.
\begin{figure}
  \thisfloatpagestyle{empty}
  \vspace{-5cm}
  \makebox[\textwidth][c]{\includegraphics[height=.7\paperheight]{biology-data/STATS13734/data_viz}}
  \caption[CIS infection episodes]{%
    500 randomly selected infection episodes.
    Shown are the negative tests before and after the outermost positive tests associated with the episode.
    Red dots are negative tests, green dots are positive tests, and blue dots are void tests (where the result could not be determined; excluded from other analyses).
